---
title: "Stat 250 Project"
author: "İrem Ekmekçi"
output: word_document
---


```{r}
library(ggplot2)
Bank <- read.csv("~/Desktop/Bank_credit.csv")
head(Bank)
str(Bank)
summary(Bank)
Bank<-na.omit(Bank)
head(Bank)
```

#Which property area has the highest frequency?

```{r}
Property_Area<-table(Bank$Property_Area)
barplot(Property_Area,col = c("coral3","dodgerblue3","plum3"),main="Bar Plot of Property Areas",)
text(Property_Area,labels = Property_Area)
```


#Is the average coapplicant income greater than 1500 or not?

```{r}
shapiro.test(Bank$CoapplicantIncome)
t.test(Bank$CoapplicantIncome,alternative = "greater",mu=1500)
library(BSDA)
SIGN.test(Bank$CoapplicantIncome,md=1500,alt="greater")

```

#Is the average loan amount equal to 125$?
```{r}
shapiro.test(Bank$LoanAmount)
t.test(Bank$LoanAmount,alternative = "two.sided",mu=125)
library("BSDA")
SIGN.test(Bank$LoanAmount,md=125,alt="two.sided")
```



#Is the average applicant income significantly higher for applicants who are graduate to not graduate?
```{r}
Graduate<-Bank$ApplicantIncome[Bank$Education=="Graduate"]
Graduate
shapiro.test(Graduate)
NotGraduate<-Bank$ApplicantIncome[Bank$Education=="Not Graduate"]
NotGraduate
shapiro.test(NotGraduate)
var.test(Graduate,NotGraduate)
t.test(Graduate,NotGraduate,alternative="greater",conf.level = 0.95)
wilcox.test(Graduate,NotGraduate, paired = F, alternative="greater", mu = 0)
```


#Is the average loan amount the same for all property areas?

```{r}
boxplot(Bank$LoanAmount~Bank$Property_Area,main="The Box Plot of Loan Amount with respect to Propert Area",xlab = "Property Areas",ylab = "Loan Amount",col=c("red","slateblue","lightcoral"))
shapiro.test(Bank$LoanAmount[Bank$Property_Area=="Rural"])
shapiro.test(Bank$LoanAmount[Bank$Property_Area=="Semiurban"])
shapiro.test(Bank$LoanAmount[Bank$Property_Area=="Urban"])
bartlett.test(LoanAmount~Property_Area,data=Bank)
fit<-aov(LoanAmount~Property_Area,data=Bank)
summary(fit)
kw.test(LoanAmount~Property_Area,data=Bank)
```


#Is there a linear relationship between loan amount and other variables?
```{r}
cont.bank<-Bank[,c(7:11)]
Corrtable<-cor(cont.bank)
Corrtable
library(corrplot)
corrplot(Corrtable)
ggplot(Bank,aes(x=ApplicantIncome,y=LoanAmount)) + geom_point(col="salmon")+ labs(title="Relationship Between Applicant Income and Loan Amount",xlab="Applicant Income",ylab="Loan Amount")+theme_bw()
cor(Bank$ApplicantIncome,Bank$LoanAmount)
ggplot(Bank,aes(x=CoapplicantIncome,y=LoanAmount)) + geom_point(col="slateblue")+ labs(title="Relationship Between Coapplicant Income and Loan Amount",xlab="Coapplicant Income",ylab="Loan Amount")+theme_bw()
cor(Bank$CoapplicantIncome,Bank$LoanAmount)
fit=lm(LoanAmount~Gender+Married+Education+Self_Employed+ApplicantIncome+CoapplicantIncome,data=Bank)
summary(fit)
par(mfrow=c(2,2))
plot(fit)
fit2=lm(LoanAmount~Married+Education+ApplicantIncome+CoapplicantIncome,data=Bank)
summary(fit2)
library(DAAG)
vif(fit2)
par(mfrow=c(2,2))
plot(fit2)

```

